WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2019-03-06 review/referee_response_0.txt

The authors present a number of new and high-quality transit observations of
the hot Jupiter WASP-4b observed by TESS. After comparing the predicted
mid-transit times (obtained only considering the pre-existing transits in the
literature) with the measured values from the TESS light curves, the authors
conclude that the TESS transits occur ~ 82 seconds earlier than predicted. They
examine different possibilities and find that the 2 most favored scenarios to
explain this deviation are orbital decay and apsidal precession. However, the
authors caution that more observations are needed to confirm these results.
Also, they redetermine various parameters of the system, finding them in
general agreement with literature values.

In general, the manuscript is scientifically accurate and the results presented
in it certainly will be of interest to other investigators in the field. Then,
I consider this paper worthy of being published after the concerns described
below be addressed.

Below are my comments, beginning with the major points. I recommend the authors
take them into consideration when revising their manuscript.

  > RESPONSE: We thank the referee for this summary. In our revision, we
  > have added weight to a third possible explanation that we previously
  > mentioned but did not sufficiently emphasize: a massive outer
  > companion, perhaps on an eccentric orbit, might be able to explain
  > both the transit and radial velocity observations. We have
  > described this possibility throughout the text where appropriate.
  > We also added our own re-analysis of the extant RV data
  > (now section 4.3, and figure 6) to check on the Knutson et al
  > (2014) result that the star's acceleration towards our line of sight
  > is only weakly detected, and is an order of magnitude too small to
  > explain the observed period derivative from the transit times.

@@

2. NEW TRANSITS AND SYSTEM PARAMETERS:

Section 2.1:

i) It could be informative to provide a reference for the "Deep Space Network".

  > RESPONSE: We are not aware of any paper that suits the purpose here,
  > so we added a citation to the URL of the Deep Space Network.

@@

iv) To estimate transit times for each individual lightcurve, did the authors
use the same code as for the phase-folded light curve? In this case, how were
the mid-transit times' uncertainties determined?

  > RESPONSE: This is discussed in paragraphs 3 and 4 of Section 2.2:

    > """To measure the transit times, we returned to the `cleaned' PDC
    > time series and fitted the data within four transit durations of
    > each transit separately. We used four free parameters: the time of
    > mid-transit $t_{\rm tra}$, the planet-to-star radius ratio, and the
    > slope and intercept of a linear trend to account for any slow
    > variations unrelated to the transit.  We fixed the remaining
    > parameters at the values that had been determined from the
    > phase-folded TESS lightcurve.  The uncertainty in each
    > \added{photometric} data point was set equal to the
    > root-mean-square (rms) level of the out-of-transit data.
    > 
    > To verify that the measured uncertainties are estimated accurately,
    > we computed the reduced $\chi^2$ for a linear ephemeris fit to the
    > measured TESS mid-transit times.  We found that $\chi^2 = 9.2$,
    > with $n=16$ degrees of freedom.  The variance of the $\chi^2$
    > distribution is $2n$, so we would expect $\chi^2 = 16 \pm 5.7$.
    > Visually inspecting the residuals showed that the error variance
    > had been overestimated, so we multiplied the measured TESS errors
    > by a factor $f=0.76$, forcing a reduced $\chi^2$ of unity.  This
    > lowered the mean uncertainty of the transit midtimes from $29.8$ to
    > $22.6$ seconds.  We verified that omitting this step did not
    > appreciably alter any of our conclusions."""

  > In short, we used the same transit model as before (the BATMAN
  > code), but with the addition of the slope and intercept of a
  > linear trend as free parameters.  Our proceduring for
  > determining the mid-transit time uncertainties is also
  > described.

### 2019-03-06 paper/ms.tex
fix typos in d1984d4d5df426e0f423d67c48df9de8f4627960

Although the Transiting Exoplanet Survey Satellite (TESS\added{,
\citealt{ricker_transiting_2015}}) is designed to detect new planets,
it is also \replaced{performing precise photometric monitoring
of}{precisely monitoring} most of the planets that have been
discovered by ground-based transit surveys over the last two decades.
One \replaced{of the applications}{application} of the new TESS data
is to search for timing anomalies in \added{previously known }hot
Jupiter systems.  Long-term monitoring of hot Jupiter transit and
occultation times should eventually reveal \replaced{two
distinct}{variations caused by three different} \replaced{processes}{phenomena}.

@@

With spots injected, we repeated our measurement of the transit times.
On average, the measured transit times did not change after injecting spots,
because the flux deviations are equally likely to occur
in the first and second halves of the transit. 
For individual transits, there were no cases for which the
timing deviation was larger than one minute.  The largest 
shifts occur when the spot anomaly occurs during transit ingress or egress, in
which case the measured mid-time is shifted early by between 30 and 50
seconds \citep[qualitatively similar to results found
by][]{ioannidis_how_2016}.

>>>>

Although the Transiting Exoplanet Survey Satellite (TESS\added{,
\citealt{ricker_transiting_2015}}) is designed to detect new planets,
it is also \replaced{performing precise photometric monitoring
of}{precisely monitoring} most of the planets that have been
discovered by ground-based transit surveys over the last two decades.
One \replaced{of the applications}{application} of the new TESS data
is to search for timing anomalies in \added{previously known }hot
Jupiter sytems.  Long-term monitoring of hot Jupiter transit and
occultation times should eventually reveal \replaced{two distinct
processes}{variations caused by three different phenomena}.

@@

With spots injected, we repeated our measurement of the transit times.
On average, the measured transit times did not change after injecting
spots, because the flux deviations are equally likely to occur in the
first and second halves of the transit.  For individual transits,
there were no cases for which the timing deviation was larger than one
minute.  The largest shifts occur when the spot anomaly occurs during
transit ingress or egress, in which case the measured mid-time is
shifted either late or early by between 30 and 50 seconds
\citep[qualitatively similar to results found
by][]{ioannidis_how_2016}.
